Practicing with the data

### 2017-07-21 practice.Rmd
started making the code more reproducible

---
title: "Practicing with the data"
author: "Lisa Oshita"
date: "June 29, 2017"
output:
  html_document: default
  pdf_document: default
---
```{r}
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))
```

### Creating time to event variable
censoring indicator variable: answered
```{r}
out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

#subsetting to include only questions in english
library(dplyr)
out_english <- out %>% 
                tbl_df() %>% 
                filter(langid == "en")
```

### exploring time to event variable
```{r}
summary(out_english$time_until_answer)

@@

#defining tick marks for x-axis
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

require(scales)
ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous(labels = comma, breaks = seq(min, max, by = (max-min)/10)) + 
  theme(axis.text.x = element_text(angle=90, hjust=1))

#zoomed in histogram of responses
ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(20, 30000))

#changing y axis on the boxplot
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

boxplot(out_english$time_until_answer, ylab = "Time until answer", yaxt = "n")
axis(side = 2, at = seq(min, max, by = (max-min)/10), las = 2, cex.axis = 0.5)
boxplot.stats(out_english$time_until_answer)
#797 questions lie outside of the whiskers
```

@@

#view average time until answered grouped by each category 
out_english%>%
  group_by(category) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(avg_time)

#looking at median time_until_answer since data is skewed right
out_english%>%
  group_by(category) %>%
  summarise(median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(median_time)

@@

#examining avg/median text length and comparing it to avg time_until_answer for each category
out_english %>%
  group_by(category) %>%
  summarise(avg = mean(text_length), median = median(text_length), avg_time = mean(time_until_answer), n = n()) %>%
  arrange(avg_time)
```

@@

### number of pictures included 
```{r}
summary(out_english$n_images)
hist(out_english$n_images)
table(out_english$n_images)

#proportion of questions that include any images
sum(out_english$n_images != 0)/nrow(out_english)

#looking at mean time_until_answer grouped by n_images
out_english %>% 
  group_by(as.factor(n_images)) %>%
  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
  arrange(avg_time)

#looking at mean time_until_answer grouped by categories and n_images
out_english %>%
  group_by(category, as.factor(n_images)) %>%
  summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
  arrange(category, avg_time)

#looking at whether or not a question included at least one pic
#creating the variable
sum(out_english$pic_included)/length(out_english$pic_included)

out_english$pic_included <- 0
out_english$pic_included[out_english$n_images != 0] <- 1

out_english %>%
  group_by(as.factor(pic_included)) %>%
  summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
  arrange(avg_time)

@@

#indicator variable for whether or not the question was categorized correctly
out_english$categorized <- 0
out_english$categorized[!is.na(out_english$category)] <- 1
out_english %>%
  tbl_df %>%
  group_by(as.factor(categorized)) %>%
  summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
  arrange(desc(avg_dailyviews))
```

>>>>

---
title: "Practicing with the data"
author: "Lisa Oshita"
date: "June 29, 2017"
output:
  html_document: default
  pdf_document: default
---
#### Importing the data/Setting up time to event variable
```{r}

dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

library(dplyr)
out_english <- out %>% 
                tbl_df() %>%
                filter(langid == "en")

out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
empty <- which(is.na(out_english$time_until_answer))
for (i in empty) {
  out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}

proportion_answered <- sum(out_english$answered)/nrow(out_english)
```

#### About the data set
* `r nrow(out_english)` observations
* `r proportion_answered * 100` % of questions were answered

#### time until answer 
* minimum: `r summary[1]` hrs
* maximum: `r summary[6]` hrs
* mean: `r summary[4]` hrs
* median: `r summary[3]` hrs
* first quartile: `r summary[2]`hrs
    + 25% of the questions were answered by `r summary[2]` hrs
* third quartile: `r summary[5]` hrs
    + 75% of the questions were answered by `r summary[5]` hrs
* IQR range: `r summary[5] - summary[2]` hrs

```{r}
summary <- summary(out_english$time_until_answer)

@@

ggplot(out_english, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)", labels = comma) 
```

@@

#view average time until answered grouped by each category 
out_english%>%
  group_by(category) %>%
  summarise(avg_time = mean(time_until_answer, na.rm = TRUE), median_time = median(time_until_answer, na.rm = TRUE), num = n()) %>%
  arrange(avg_time)

@@

#examining avg/median text length and comparing it to avg time_until_answer for each category
out_english %>%
  group_by(category) %>%
  summarise(avg = mean(text_length), median = median(text_length), median_time = median(time_until_answer), n = n()) %>%
  arrange(median_time)
```

@@

### number of pictures included 
```{r}
# summary(out_english$n_images)
# hist(out_english$n_images)
# table(out_english$n_images)
# 
# #proportion of questions that include any images
# sum(out_english$n_images != 0)/nrow(out_english)
# 
# #looking at mean time_until_answer grouped by n_images
# out_english %>% 
#   group_by(as.factor(n_images)) %>%
#   summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
#   arrange(avg_time)
# 
# #looking at mean time_until_answer grouped by categories and n_images
# out_english %>%
#   group_by(category, as.factor(n_images)) %>%
#   summarise(avg_time = mean(time_until_answer), median = median(time_until_answer), n = n()) %>%
#   arrange(category, avg_time)
# 
# #looking at whether or not a question included at least one pic
# #creating the variable
# sum(out_english$pic_included)/length(out_english$pic_included)
# 
# out_english$pic_included <- 0
# out_english$pic_included[out_english$n_images != 0] <- 1
# 
# out_english %>%
#   group_by(as.factor(pic_included)) %>%
#   summarise(avg_time = mean(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
#   arrange(avg_time)

@@

#indicator variable for whether or not the question was categorized correctly
# out_english$categorized <- 0
# out_english$categorized[!is.na(out_english$category)] <- 1
# out_english %>%
#   tbl_df %>%
#   group_by(as.factor(categorized)) %>%
#   summarise(avg_dailyviews = mean(daily_views), median = median(daily_views), avg_time = mean(time_until_answer), n = n()) %>%
#   arrange(desc(avg_dailyviews))
```
